Molecular dynamics simulation of synchronization in driven particles

### 2021-02-20 manuscript/manuscript_ajp_2020.tex
moved Fdc to fig3 and have level steps now!
updated Brownian figure - some text to update

%the average velocity of the particle
%is constant 
%despite the overall magnitude
%of $F^{dc}$.
Each step represents a different pattern of hops
between substrate minima
performed by the particle
due to the landscape confinement.  
In Fig.~\ref{fig:1} at %this occurs at 
low $F^{dc}$ the average velocity $\langle v_y \rangle$ is zero.
Since 
$A_p$ is large compared to the extrema of $F^{D}(t)$,
the particle oscillates back and forth
in a single minima with no net velocity.
At higher $F^{dc}$ the particle velocity 
$\langle v_{y} \rangle$ increases in steps of uniform height,
$\langle v_{y} \rangle = n \lambda f$,
where $n$ is an integer.
The step width is non-linear 
and can have a variety of
interesting patterns
such as a devil's staircase related to chaotic dynamics \cite{Bak1986}.
We note the individual steps
are not strictly horizontal 
since particles move continuously
through the landscape, so changes in $F^{dc}$
will create linear changes in 
net particle displacement that are observable
within a single step.
\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{sweep_FDC_vs_vx.pdf}
\caption{Average particle velocity  $\langle v_{y} \rangle$ as a function of $F^{dc}$,
  the constant parameter of $F^D(t)$ defined in Eq.~\ref{eq:drive}.
  The remaining parameters in $F^D(t)$ are as in Fig.~\ref{fig:0}, $F^{ac}=0.05$ and $f = 0.01$.  }
\label{fig:1}
\end{figure}
\end{center}
%$\lambda = L/N_p = 36.5/20 = 1.825$ is the spatial period, or wavelength
%of the landscape,
%and $f = 0.01$ cycles per time unit.
%This synchronization
%of the particle velocity can be measured
%in terms of the landscape period.
%Phase locked steps occur for average displacements integer
%multiples of the substrate period $n\lambda$.
%\subsection{Phase plots}
%  \label{ex:phase}

@@

  {\bf With no applied driving force,
    find 
  the minimum temperature required for a single particle
  to hop over maxima in the potential landscape.}
  %$T_{min} > A_p$.
  Assume the particle is confined to
  move along the $y-$direction,
  include Brownian motion 
  in the model.
  In Fig.~\ref{fig:brownian},
  we demonstrate the transition
  from pinned to hopping
  in 
  %Measure the position vs. time
  a non-driven colloid for $T/A_p = 4.0$, $5.0$, and $6.0$.
  The crossover
  to a hopping regime occurs at $T/A_p \approx 5.6$.
  %Reproduce these results.  
  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{brownian_particle_dt0.1}.pdf}
      \caption{
        Motion of a particle undergoing Brownian motion
        on a washboard potential
        energy landscape.
        (a) $T/A_p = 4.0$ no hopping occurs.
        (b) $T/A_p = 5.0$ a three hops occur %at $t = 130000$
        across distances of $\Delta y = 2 \lambda$.
        (c) $T/A_p = 6.0$ many hops occur.
        Note the scale of the $y-$axis differs in each panel
        and the time scale is
        much greater than in Fig.~\ref{fig:0}.
      }
      \label{fig:brownian}
    \end{figure}
  \end{center}
  In Fig.~\ref{fig:brownian}
  we show the position versus time of a particle
  confined to a sinusoidal landscape
  undergoing Brownian motion.
  We increase the temperature relative
  to the amplitude of the landscape
  troughs until the particle enters a hopping regime.
  In  Fig.~\ref{fig:brownian}(a)
  the temperature is $T/A_p = 4.0$.
  The particle executes a 
  random walk centered at the potential minima $y/\lambda = 10$.
  We ran many simulations and never observed a hop to another minima
  within this simulation time.  
  In  Fig.~\ref{fig:brownian}(b)
  $T/A_p = 5.0$,  hops between
  potential minima are possible but not probable,
  a back-forth hop occurs from
  $y/\lambda = 10$ to $12$ at
  $t \sim 40000 \tau$ and a single hop from 
  $y/\lambda = 10$ to $8$ occurs at
  $t \sim 280000 \tau$.
  In other simulations with identical parameters,
  we sometimes observed no hops or two hops between minima,
  as expected with random fluctuating systems.
  In  Fig.~\ref{fig:brownian}(c)
  $T/A_p = 6.0$ 
  we observe many hops.
  The random thermalized kicks are
  sufficiently large to make the particle perform
  what appears to be 
  a random walk of hops atop the substrate.
  [prove it]
  %in addition to the small scale random walk executed
  %by all particles in this section.

>>>>

%the average velocity of the particle
%is constant 
%despite the overall magnitude
%of $F^{dc}$.
Each step represents a different pattern of hops
between substrate minima
performed by the particle
due to the landscape confinement.  
In Fig.~\ref{fig:1} at %this occurs at 
low $F^{dc}$ the average velocity $\langle v_y \rangle$ is zero.
Since 
$A_p$ is large compared to the extrema of $F^{D}(t)$,
the particle oscillates back and forth
in a single minima with no net velocity.
At higher $F^{dc}$ the particle velocity 
$\langle v_{y} \rangle$ increases in steps of uniform height,
$\langle v_{y} \rangle = n \lambda f$,
where $n$ is an integer.
The step width is non-linear 
and can have a variety of
interesting patterns
such as a devil's staircase related to chaotic dynamics \cite{Bak1986}.
We note the individual steps
are not strictly horizontal 
since particles move continuously
through the landscape, so changes in $F^{dc}$
will create linear changes in 
net particle displacement that are observable
within a single step.
\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{fig3.pdf}
\caption{Average particle velocity  $\langle v_{y} \rangle$
  as a function of $F^{dc}$, 
  the constant parameter of $F^D(t)$ defined in Eq.~\ref{eq:drive}.
  We fix
  $F^{ac}=0.0$ (blue) and 
  $F^{ac}=0.05$ (orange) with $f = 0.01$ 
  as in Fig.~\ref{fig:0}.}
\label{fig:1}
\end{figure}
\end{center}
%$\lambda = L/N_p = 36.5/20 = 1.825$ is the spatial period, or wavelength
%of the landscape,
%and $f = 0.01$ cycles per time unit.
%This synchronization
%of the particle velocity can be measured
%in terms of the landscape period.
%Phase locked steps occur for average displacements integer
%multiples of the substrate period $n\lambda$.
%\subsection{Phase plots}
%  \label{ex:phase}

@@

  {\bf With no applied driving force,
    find 
  the minimum temperature required for a single particle
  to hop over maxima in the potential landscape.}
  %$T_{min} > A_p$.
  Assume the particle is confined to
  move along the $y-$direction,
  include Brownian motion 
  in the model.
  In Fig.~\ref{fig:brownian},
  we demonstrate the transition
  from pinned to hopping
  in 
  %Measure the position vs. time
  a non-driven colloid for $T/A_p = 3.0$, $3.5$, and $4.0$.
  %The crossover
  %to a hopping regime occurs at $T/A_p \approx 5.6$.
  %Reproduce these results.  
  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{fig4}.pdf}
      \caption{
        Motion of a particle undergoing Brownian motion
        on a washboard potential
        energy landscape.
        (a) $T/A_p = 3.0$ no hopping occurs.
        (b) $T/A_p = 3.5$ one hop occurs and %at $t = 130000$
        %across distances of $\Delta y = 2 \lambda$.
        (c) $T/A_p = 4.0$ many hops occur.
        Note the scale of the $y-$axis differs in each panel
        and the time scale is
        greater than in Fig.~\ref{fig:0}.
        The precise timing of hops pattern varies
        by simulation,
        sometimes exhibiting several hops for $T/A_p = 3.5$. 
      }
      \label{fig:brownian}
    \end{figure}
  \end{center}
  In Fig.~\ref{fig:brownian}
  we show the position versus time of a particle
  confined to a sinusoidal landscape
  undergoing Brownian motion.
  We increase the temperature relative
  to the amplitude of the landscape
  troughs until the particle enters a hopping regime.
  In  Fig.~\ref{fig:brownian}(a)
  the temperature is $T/A_p = 4.0$.
  The particle executes a 
  random walk centered at the potential minima $y/\lambda = 10$.
  We ran many simulations and never observed a hop to another minima
  within this simulation time.  
  In  Fig.~\ref{fig:brownian}(b)
  $T/A_p = 5.0$,  hops between
  potential minima are possible but not probable,
  a back-forth hop occurs from
  $y/\lambda = 10$ to $12$ at
  $t \sim 40000 \tau$ and a single hop from 
  $y/\lambda = 10$ to $8$ occurs at
  $t \sim 280000 \tau$.
  In other simulations with identical parameters,
  we sometimes observed no hops or two hops between minima,
  as expected with random fluctuating systems.
  In  Fig.~\ref{fig:brownian}(c)
  $T/A_p = 6.0$ 
  we observe many hops.
  The random thermalized kicks are
  sufficiently large to make the particle perform
  what appears to be 
  a random walk of hops atop the substrate.
  [prove it]
  %in addition to the small scale random walk executed
  %by all particles in this section.
